Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-15 relwork.tex
crank on section 4, nearly done, along the way adding some hybrid logic comparison stuff

>>>>

As noted throughout the paper, the inspiration for our other-space modality comes from hybrid logic~\cite{areces2001hybrid,blackburn1995hybrid,gargov1993modal,goranko1996hierarchies},
where modalities are indexed by \emph{nominals} which are names for specific individual states in a Kripke model.
We are aware of only two prior works combining hybrid logics with program logics specifically. 
Brotherston and Villard~\cite{brotherston2014parametric} demonstrated that may properties true of various 
separation logics are not definable in boolean \BI (\BBI), and showed that a hybrid extension \HyBBI allows
most such properties to be defined (e.g., the fact that separating conjunction is cancellative is unprovable 
in boolean \BI, but provable in \HyBBI). There, nominals named resources 
(roughly, but not exactly, heap fragments). 
Gordon~\cite{gordon2019modal} described a use of hybrid logic in the verification of actor programs, 
where nominals named the local state of individual actors (with such assertions stabilized with a 
rely/guarantee approach). Beyond these, there is limited work on the interaction of specifically 
\emph{hybrid logic} with substructural logics. 
Primarily there is a line of work on hybrid linear logic (\HyLL)~\cite{despeyroux2014hybrid}, 
originally used as a way to more conveniently express aspects of transition systems in linear logic. 
However, \HyLL's proof rules offer no non-trivial interactions with multiplicative connectives 
(every \HyLL proof can in fact be embedded into regular linear logic~\cite{chaudhuri2019hybrid}, 
unlike Brotherston and Villard's \HyBBI, which demonstrably increases expressive power over its base \BBI.

In both \HyLL and \HyBBI, nominals denote worlds with monoidal structure (as worlds in Kripke semantics
for either LL or \BBI necessarily have monoidal structure). Our nominals, by contrast, 
do not name worlds in the same sense with respect to Iris's CMRAs, 
but in fact \emph{classes} of worlds, because the names are locations 
(a means of \emph{selecting} resources) rather than resources.  
A key difference is that the use of nominals in those logics corresponds specifically to hypothetical 
reasoning about resources (until a nominal is connected to a current resource, in which case conclusions 
can be drawn about the current resource), which means the modalities themselves do not ``own'' resources. 
Instead, assertions under our other-space modality can and do
have resource footprints.
Pleasantly, we sidestep most of the metatheoretical complexity of those other substructural hybrid
systems by building our logic within a substructural metatheory (Iris).
